\documentclass[11pt]{article}

%%  Dimensions and URL
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

%%  Definitions
\renewcommand{\baselinestretch}{1.1}
\pagestyle{plain}


\begin{document}

\begin{center}
{\bfseries \LARGE Optional Task 2 -- Python Programming \\ and PyCharm (Educational Edition) \\[8mm]}
\end{center}


\section{The Python Programming Language}

Python is a widely used general-purpose, high-level programming language that supports mutliple programming paradigms.
Its design philosophy emphasizes code readability.
Python interpreters are available for installation on many operating systems, allowing Python code execution on a wide variety of systems.

\subsection*{Action Items}

\begin{itemize}
\item \textbf{Peruse:} The Python Software Foundation website. \\
\url{https://www.python.org}
\end{itemize}


\section{PyCharm}

PyCharm is a Python integrated development environment (IDE) for programming computer software.
It is developed by \href{https://www.jetbrains.com}{JetBrains}.
The Educational Edition is free and open source.

\subsection*{Action Items}

\begin{itemize}
\item \textbf{Read:} About PyCharm Educational Edition. \\
\url{https://www.jetbrains.com/pycharm-educational/}
\item \textbf{Watch:} Take a tour of PyCharm Educational Edition. \\
\url{https://www.youtube.com/watch?v=xCCHIfC-dtA}
\item \textbf{Download and Install:} PyCharm Educational Edition. \\
\url{https://www.jetbrains.com/pycharm-educational/}
\item \textbf{Complete:} Introduction to Python in PyCharm.
\end{itemize}


\end{document}

